A dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-07-11 ms/ms.Rmd
fig legends

![Alternate stable states in S:H biomass and growth across a light gradient. Alternate stable states occur between ~25-42 mol photons m^-2^ d^-1^ under these conditions (DIN=1e-7 mol N L^-1^; X=1e-7 C-mol X L^-1^), depending on whether initial S:H is high (1, closed circles), representing a healthy coral, or low (0.0001, open circles), representing a bleached coral. Arrow above point at L=25 indicates a S:H ratio beyond the axis range; this 'overshoot' phenomenon, in which initially  bleached corals may achieve high S:H ratios while remaining in a carbon-limited state is discussed in the *Coral Bleaching and Recovery* section.](../img/Fig2.png)

@@

![Hysteresis under different nutrient and feeding regimes. Steady state S:H biomass ratios in constant environments with (A) low DIN (1e-7 M) and low food (2e-7 M), (B) low DIN (1e-7 M) and no food, (C) high DIN (2e-6 M) and low food (2e-7 M), and (D) high DIN (2e-6 M) and high food (4e-7 M). In each panel, steady states are shown starting from both high initial S:H biomass (1, i.e. healthy corals - closed circles) and low initial initial S:H biomass (0.0001, i.e. bleached corals - open circles). Points are colored according to whether the host exhibits positive (black) or negative (red) growth at steady state.](../img/Fig8.png)

>>>>

![Alternate stable states in S:H biomass and growth across a light gradient. Alternate stable states occur between ~25-42 mol photons m^-2^ d^-1^ under these conditions (DIN=1e-7 mol N L^-1^; X=1e-7 C-mol X L^-1^), depending on whether initial S:H is high (1, closed circles), representing a healthy coral, or low (0.0001, open circles), representing a bleached coral. Arrow above point at L=25 indicates a S:H ratio beyond the y-axis range; this 'overshoot' phenomenon, in which initially  bleached corals may achieve high S:H ratios while remaining in a carbon-limited state is discussed in the *Coral Bleaching and Recovery* section.](../img/Fig2.png)

@@

![Hysteresis under different nutrient and feeding regimes. Steady state S:H biomass ratios in constant environments with (A) low DIN (1e-7 M) and low food (2e-7 M), (B) low DIN (1e-7 M) and no food, (C) high DIN (2e-6 M) and low food (2e-7 M), and (D) high DIN (2e-6 M) and high food (4e-7 M). In each panel, steady states are shown starting from both high initial S:H biomass (1, i.e. healthy corals - closed circles) and low initial initial S:H biomass (0.0001, i.e. bleached corals - open circles). Points are colored according to whether the host exhibits positive (black) or negative (red) growth at steady state. Arrows above points indicate values beyond the y-axis range.](../img/Fig8.png)
